GSEA for flash factors

### 2017-12-04 analysis/GSEA_flashr.Rmd

---
title: "compare the options for missing value MSE"
author: "Wei"
date: 2017-12-04
output: html_document
---

@@

## Movie Lens data

### FDR without null check vs default setting

```{r}
library(ggplot2)
plot_res = function(output,title = "data",legend_position = "none"){
  rmse = as.vector(output)
  N = dim(output)[1]
  methods = rep(c("flash_fdr","flash","NBSFA_fdr","NBSFA","PMD_fdr","PMD","softImpute_fdr","softImpute"), each = N)
  df = data.frame(RMSE = rmse, Method = methods )
  p<-ggplot(df, aes(x=Method, y=RMSE, color=Method)) +
  geom_boxplot()+
  # geom_violin()+
  ggtitle(title) +  theme_bw()+
    theme(legend.position= legend_position, legend.text=element_text(size=15), axis.text.y = element_text(size =6))
  p
}
data1 = readRDS("../data/cmpOptions/ML100K/FDRnocheck_box.rds")
data2 = readRDS("../data/cmpOptions/ML100K/box_defaultseeting.rds")
data1 = matrix(as.numeric(data1),ncol = 4)
data2 = matrix(as.numeric(data2),ncol = 4)
pM = plot_res(cbind(data1[,1],data2[,1],
                    data1[,2],data2[,2],
                    data1[,3],data2[,3],
                    data1[,4],data2[,4]),"Movie Lens data different settings")
pM
```

We run the experiments twice. `flash_fdr` `NSFA_fdr` `PMD_fdr` and `softImpute_fdr` stand for the results from the simulation data set with FDR method and without Nullcheck in FLASH method. And `flash` `NSFA` `PMD` and `softImpute` represent the results from simulation data set with default setting (shrink, normal with Nullcheck) in FLASH.

## GTEx EQTL Z-score

### FDR without null check vs default setting

```{r}
data1 = readRDS("../data/cmpOptions/GETxZscore/FDRnocheck_box.rds")
data2 = readRDS("../data/cmpOptions/GETxZscore/DefaultSetting_box.rds")
data1 = matrix(as.numeric(data1),ncol = 4)
data2 = matrix(as.numeric(data2),ncol = 4)
pG = plot_res(cbind(data1[,1],data2[,1],
                    data1[,2],data2[,2],
                    data1[,3],data2[,3],
                    data1[,4],data2[,4]),"GTEx z-score different settings")
pG
```

>>>>

---
title: "GSEA for flash factors"
author: "Wei"
date: 10-2017
output: html_document
---

@@

## try the 3rd factor

Here, we should preare the list of the gene names.

```{r}
res = readRDS("../data/GTEX/bflashvarcol.rds")
load("../data/GTEX/gtexEQTL_zscore.rds")
sorted_f3 = sort(res$EF[,3],index.return = T)
negative_index = sorted_f3$ix[which(sorted_f3$x<0)]
negative_name = row.names(zscore)[negative_index]
new_names = sapply(negative_name, function(x){(strsplit(x,"\\.")[[1]])[1]})
# write.table(new_names,file = "../data/GTEX/f_3_neg.txt",row.names = F,col.names = F)
```
